---
title: "Missing Migrants"
output: word_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(fitdistrplus)
library(dplyr)
library(gridExtra)
library(grid)
library(ggplot2)
library(reshape2)
migrant_df=read.csv('MissingMigrants-Global-2019-03-29T18-36-07.csv', sep=',', header=TRUE)

head(migrant_df,2)


nrow(migrant_df)

migrant_df=migrant_df %>%
  rename(WebID=ï..Web.ID)





```











```{r,include=FALSE}
descdist(c(na.exclude(migrant_df$Number.of.Survivors)))


descdist(c(na.exclude(migrant_df$Minimum.Estimated.Number.of.Missing)))

#Convert to log - Num of survivors

migrant_df$Survivors=log10((migrant_df$Number.of.Survivors)+0.1)



descdist(c(na.exclude(migrant_df$Survivors)))
fit_sur=fitdist(c(na.exclude(migrant_df$Survivors)),'norm')
summary(fit_sur)
par(mfrow=c(2,2))
plot.legend=c('Norm - Num of Survivors')
denscomp(list(fit_sur),legendtext = plot.legend,xlab='X values',xlegend='topleft')
cdfcomp(list(fit_sur),legendtext = plot.legend,xlab='X values',xlegend='topleft')
qqcomp(list(fit_sur),legendtext = plot.legend,xlab='X values',xlegend='topleft')
ppcomp(list(fit_sur),legendtext = plot.legend,xlab='X values',xlegend='topleft')
 
#Converting to log - missing num


migrant_df$Missingnum=log10((migrant_df$Minimum.Estimated.Number.of.Missing)+0.1)


descdist(c(na.exclude(migrant_df$Missingnum)))
fit_miss=fitdist(c(na.exclude(migrant_df$Missingnum)),'norm')

summary(fit_miss)
par(mfrow=c(2,2))
plot.legend=c('Norm - Num of missing people')
denscomp(list(fit_miss),legendtext = plot.legend,xlab='X values',xlegend='topleft')
cdfcomp(list(fit_miss),legendtext = plot.legend,xlab='X values',xlegend='topleft')
qqcomp(list(fit_miss),legendtext = plot.legend,xlab='X values',xlegend='topleft')
ppcomp(list(fit_miss),legendtext = plot.legend,xlab='X values',xlegend='topleft')


migrant_US <- migrant_df %>%
  dplyr::filter(Region.of.Incident=='US-Mexico Border')

migrant_NA <- migrant_df %>%
  dplyr::filter(Region.of.Incident=='North Africa')


samUS=sample_n(migrant_US,300)
samNA=sample_n(migrant_NA,300)



```
#Hypothesis testing for mean of people missing at US Mexico border vs North africa

#H0: mean of missing people at US border = mean of missing people at North africa borders
#H1: M(US) not equal M(NA)

```{r}
t.test(samUS$Missingnum,samNA$Missingnum)
```
Conclusion - The number of missing people at US Mexico Border are not same as those of North Africa.

```{r,include=FALSE}
migrant_US_2016=migrant_US %>%
  dplyr::filter(Reported.Year=='2016')

migrant_US_2017=migrant_US %>%
  dplyr::filter(Reported.Year=='2017')

sam16=sample_n(migrant_US_2016,200)
sam17=sample_n(migrant_US_2017,200)
```
#t test 
#HO
#mean of num of people survived in US Mexico 2015 = 2016
#dying due lack of medicines and sickness

#H1=not equal


```{r}
t.test(sam16$Survivors,sam17$Survivors)
```
Conclusion - The mean number of people who survived in US-Mexico border in 2016 is same as those who survived in 2017.


```{r,include=FALSE}
migrantNA <- migrant_df %>%
  dplyr::filter(Region.of.Incident=='North Africa')

NA_D_2016<- migrantNA %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Number.Dead) %>%
  dplyr::filter(Reported.Year=='2016') %>%
  group_by(Reported.Date) %>%
  summarise(NumDead1=sum(Number.Dead,na.rm=1)) %>%
  group_by(NumDead1) %>%
  summarise(freq1=n()) %>%
  mutate(pmf_dead1=freq1/sum(freq1)) %>%
  mutate(cdf_dead1=cumsum(pmf_dead1)) 



#2017
NA_D_2017<- migrantNA %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Number.Dead) %>%
  dplyr::filter(Reported.Year=='2017') %>%
  group_by(Reported.Date) %>%
  summarise(NumDead2=sum(Number.Dead,na.rm=1)) %>%
  group_by(NumDead2) %>%
  summarise(freq2=n()) %>%
  mutate(pmf_dead2=freq2/sum(freq2)) %>%
  mutate(cdf_dead2=cumsum(pmf_dead2)) 



#2018
NA_D_2018<- migrantNA %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Number.Dead) %>%
  dplyr::filter(Reported.Year=='2018') %>%
  group_by(Reported.Date) %>%
  summarise(NumDead3=sum(Number.Dead,na.rm=1)) %>%
  group_by(NumDead3) %>%
  summarise(freq3=n()) %>%
  mutate(pmf_dead3=freq3/sum(freq3)) %>%
  mutate(cdf_dead3=cumsum(pmf_dead3)) 



#2019
NA_D_2019<- migrantNA %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Number.Dead) %>%
  dplyr::filter(Reported.Year=='2019') %>%
  group_by(Reported.Date) %>%
  summarise(NumDead4=sum(Number.Dead,na.rm=1)) %>%
  group_by(NumDead4) %>%
  summarise(freq4=n()) %>%
  mutate(pmf_dead4=freq4/sum(freq4)) %>%
  mutate(cdf_dead4=cumsum(pmf_dead4)) 




#PMF - Dead in NA
p1=ggplot(NA_D_2016,aes(NumDead1,pmf_dead1))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2016')
p2=ggplot(NA_D_2017,aes(NumDead2,pmf_dead2))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2017')
p3=ggplot(NA_D_2018,aes(NumDead3,pmf_dead3))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2018')
p4=ggplot(NA_D_2019,aes(NumDead4,pmf_dead4))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2019')

```


Probability Distributions for number of deaths -

1. PMF of North Africa region deaths -


```{r,echo=FALSE}
grid.arrange(p1,p2,p3,p4,
             top = textGrob('PMF of North Africa - Num of deaths per day (Yearwise)'))

```

2. CDF of North Africa region deaths -

```{r,include=FALSE}
p5=ggplot(NA_D_2016,aes(NumDead1,cdf_dead1))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2016')
p6=ggplot(NA_D_2017,aes(NumDead2,cdf_dead2))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2016')
p7=ggplot(NA_D_2018,aes(NumDead3,cdf_dead3))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2016')
p8=ggplot(NA_D_2019,aes(NumDead4,cdf_dead4))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2016')

```
```{r,echo=FALSE}
grid.arrange(p5,p6,p7,p8,
             top = textGrob('CDF of North Africa - Num of deaths per day (Yearwise)'))

```

3. PDF of total number of missing and dead in North Africa -

```{r,include=FALSE}
migrantNA <- migrant_df %>%
  dplyr::filter(Region.of.Incident=='North Africa')

NA_M_2016<- migrantNA %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Total.Dead.and.Missing) %>%
  dplyr::filter(Reported.Year=='2016') %>%
  group_by(Reported.Date) %>%
  summarise(NumM1=sum(Total.Dead.and.Missing,na.rm=1)) %>%
  group_by(NumM1) %>%
  summarise(freqM1=n()) %>%
  mutate(pmf_miss1=freqM1/sum(freqM1)) %>%
  mutate(cdf_miss1=cumsum(pmf_miss1)) 

NA_M_2017<- migrantNA %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Total.Dead.and.Missing) %>%
  dplyr::filter(Reported.Year=='2017') %>%
  group_by(Reported.Date) %>%
  summarise(NumM2=sum(Total.Dead.and.Missing,na.rm=1)) %>%
  group_by(NumM2) %>%
  summarise(freqM2=n()) %>%
  mutate(pmf_miss2=freqM2/sum(freqM2)) %>%
  mutate(cdf_miss2=cumsum(pmf_miss2)) 

NA_M_2018<- migrantNA %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Total.Dead.and.Missing) %>%
  dplyr::filter(Reported.Year=='2018') %>%
  group_by(Reported.Date) %>%
  summarise(NumM3=sum(Total.Dead.and.Missing,na.rm=1)) %>%
  group_by(NumM3) %>%
  summarise(freqM3=n()) %>%
  mutate(pmf_miss3=freqM3/sum(freqM3)) %>%
  mutate(cdf_miss3=cumsum(pmf_miss3)) 

NA_M_2019<- migrantNA %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Total.Dead.and.Missing) %>%
  dplyr::filter(Reported.Year=='2019') %>%
  group_by(Reported.Date) %>%
  summarise(NumM4=sum(Total.Dead.and.Missing,na.rm=1)) %>%
  group_by(NumM4) %>%
  summarise(freqM4=n()) %>%
  mutate(pmf_miss4=freqM4/sum(freqM4)) %>%
  mutate(cdf_miss4=cumsum(pmf_miss4)) 

#PMF - Tot Deaths and missing people in NorthAfrica

p9=ggplot(NA_M_2016,aes(NumM1,pmf_miss1))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2016')
p10=ggplot(NA_M_2017,aes(NumM2,pmf_miss2))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2017')
p11=ggplot(NA_M_2018,aes(NumM3,pmf_miss3))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2018')
p12=ggplot(NA_M_2019,aes(NumM4,pmf_miss4))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2019')

```
```{r,echo=FALSE}
grid.arrange(p9,p10,p11,p12,
             top = textGrob('PMF of North Africa - Total missing and dead per day (Yearwise)'))

```

4. CDF of total number of deaths and missing people in North Africa -




```{r,include=FALSE}
p13=ggplot(NA_M_2016,aes(NumM1,cdf_miss1))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2016')
p14=ggplot(NA_M_2017,aes(NumM2,cdf_miss2))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2017')
p15=ggplot(NA_M_2018,aes(NumM3,cdf_miss3))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2018')
p16=ggplot(NA_M_2019,aes(NumM4,cdf_miss4))+
  geom_bar(stat='identity',fill='blue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2019')
```



```{r,echo=FALSE}
grid.arrange(p13,p14,p15,p16,
             top = textGrob('CDF of North Africa - Total missing and dead per day (Yearwise)'))
```

5. PMF of number of people who died at US Mexico border per day -
```{r,include=FALSE}

migrantUS <- migrant_df %>%
  dplyr::filter(Region.of.Incident=='US-Mexico Border')

US_D_2016<- migrantUS %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Number.Dead) %>%
  dplyr::filter(Reported.Year=='2016') %>%
  group_by(Reported.Date) %>%
  summarise(NumDeadU1=sum(Number.Dead,na.rm=1)) %>%
  group_by(NumDeadU1) %>%
  summarise(freqU1=n()) %>%
  mutate(pmf_deadU1=freqU1/sum(freqU1)) %>%
  mutate(cdf_deadU1=cumsum(pmf_deadU1)) 

US_D_2017<- migrantUS %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Number.Dead) %>%
  dplyr::filter(Reported.Year=='2017') %>%
  group_by(Reported.Date) %>%
  summarise(NumDeadU2=sum(Number.Dead,na.rm=1)) %>%
  group_by(NumDeadU2) %>%
  summarise(freqU2=n()) %>%
  mutate(pmf_deadU2=freqU2/sum(freqU2)) %>%
  mutate(cdf_deadU2=cumsum(pmf_deadU2)) 

US_D_2018<- migrantUS %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Number.Dead) %>%
  dplyr::filter(Reported.Year=='2018') %>%
  group_by(Reported.Date) %>%
  summarise(NumDeadU3=sum(Number.Dead,na.rm=1)) %>%
  group_by(NumDeadU3) %>%
  summarise(freqU3=n()) %>%
  mutate(pmf_deadU3=freqU3/sum(freqU3)) %>%
  mutate(cdf_deadU3=cumsum(pmf_deadU3)) 

US_D_2019<- migrantUS %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Number.Dead) %>%
  dplyr::filter(Reported.Year=='2019') %>%
  group_by(Reported.Date) %>%
  summarise(NumDeadU4=sum(Number.Dead,na.rm=1)) %>%
  group_by(NumDeadU4) %>%
  summarise(freqU4=n()) %>%
  mutate(pmf_deadU4=freqU4/sum(freqU4)) %>%
  mutate(cdf_deadU4=cumsum(pmf_deadU4)) 

#PMF US Mex deaths

u1=ggplot(US_D_2016,aes(NumDeadU1,pmf_deadU1))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2016')
u2=ggplot(US_D_2017,aes(NumDeadU2,pmf_deadU2))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2017')
u3=ggplot(US_D_2018,aes(NumDeadU3,pmf_deadU3))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2018')
u4=ggplot(US_D_2019,aes(NumDeadU4,pmf_deadU4))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2019')

```

```{r,echo=FALSE}
grid.arrange(u1,u2,u3,u4,
             top = textGrob('PMF of US Mexico region - Num of deaths per day (Yearwise)'))
```

6. CDF of number of deaths at US Mexico border -

```{r,include=FALSE}
u5=ggplot(US_D_2016,aes(NumDeadU1,cdf_deadU1))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2016')
u6=ggplot(US_D_2017,aes(NumDeadU2,cdf_deadU2))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2017')
u7=ggplot(US_D_2018,aes(NumDeadU3,cdf_deadU3))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2018')
u8=ggplot(US_D_2019,aes(NumDeadU4,cdf_deadU4))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2019')

```
```{r,echo=FALSE}
grid.arrange(u5,u6,u7,u8,
             top = textGrob('CDF of US Mexico region - Num of deaths per day (Yearwise)'))

```

7. PMF of total number of deaths and missing people around US-Mexico Border-

```{r,include=FALSE}
US_M_2016<- migrantUS %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Total.Dead.and.Missing) %>%
  dplyr::filter(Reported.Year=='2016') %>%
  group_by(Reported.Date) %>%
  summarise(NummissU1=sum(Total.Dead.and.Missing,na.rm=1)) %>%
  group_by(NummissU1) %>%
  summarise(freqmU1=n()) %>%
  mutate(pmf_deadmU1=freqmU1/sum(freqmU1)) %>%
  mutate(cdf_deadmU1=cumsum(pmf_deadmU1)) 

US_M_2017<- migrantUS %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Total.Dead.and.Missing) %>%
  dplyr::filter(Reported.Year=='2017') %>%
  group_by(Reported.Date) %>%
  summarise(NummissU2=sum(Total.Dead.and.Missing,na.rm=1)) %>%
  group_by(NummissU2) %>%
  summarise(freqmU2=n()) %>%
  mutate(pmf_deadmU2=freqmU2/sum(freqmU2)) %>%
  mutate(cdf_deadmU2=cumsum(pmf_deadmU2))

US_M_2018<- migrantUS %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Total.Dead.and.Missing) %>%
  dplyr::filter(Reported.Year=='2018') %>%
  group_by(Reported.Date) %>%
  summarise(NummissU3=sum(Total.Dead.and.Missing,na.rm=1)) %>%
  group_by(NummissU3) %>%
  summarise(freqmU3=n()) %>%
  mutate(pmf_deadmU3=freqmU3/sum(freqmU3)) %>%
  mutate(cdf_deadmU3=cumsum(pmf_deadmU3))

US_M_2019<- migrantUS %>%
  dplyr::select(Region.of.Incident,Reported.Year,Reported.Date,Reported.Month,Total.Dead.and.Missing) %>%
  dplyr::filter(Reported.Year=='2019') %>%
  group_by(Reported.Date) %>%
  summarise(NummissU4=sum(Total.Dead.and.Missing,na.rm=1)) %>%
  group_by(NummissU4) %>%
  summarise(freqmU4=n()) %>%
  mutate(pmf_deadmU4=freqmU4/sum(freqmU4)) %>%
  mutate(cdf_deadmU4=cumsum(pmf_deadmU4))


#PMF Deaths and missing US Mexico
u9=ggplot(US_M_2016,aes(NummissU1,pmf_deadmU1))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2016')
u10=ggplot(US_M_2017,aes(NummissU2,pmf_deadmU2))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2017')
u11=ggplot(US_M_2018,aes(NummissU3,pmf_deadmU3))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2018')
u12=ggplot(US_M_2019,aes(NummissU4,pmf_deadmU4))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2019')
```
```{r,echo=FALSE}
grid.arrange(u9,u10,u11,u12,
             top = textGrob('PMF of US Mexico region - Total deaths and missing per day (Yearwise)'))
```


8. CDF of total number of deaths and missing people near US-Mexico border 

```{r,include=FALSE}
u13=ggplot(US_M_2016,aes(NummissU1,cdf_deadmU1))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2016')
u14=ggplot(US_M_2017,aes(NummissU2,cdf_deadmU2))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2017')
u15=ggplot(US_M_2018,aes(NummissU3,cdf_deadmU3))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2018')
u16=ggplot(US_M_2019,aes(NummissU4,cdf_deadmU4))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Number of People',y='Probability')+
  ggtitle('2019')
```
```{r,echo=FALSE}
grid.arrange(u13,u14,u15,u16,
             top = textGrob('CDF of US Mexico region - Total deaths and missing per day (Yearwise)'))
```

Correlation Statistics :

Correlation between 2016 and 2017 deaths at US Mexico border -

```{r}
cor.test(head(US_M_2016$freqmU1,6),head(US_M_2017$freqmU2,6))
```

This suggests that the death count in 2016 is highly correlated to the death count in 2017.


2. Correlation between 2017 and 2018 deaths at US Mexico border -

```{r}
cor.test(head(US_M_2017$freqmU2,6),head(US_M_2018$freqmU3,6))
```

So, the number of deaths in 2017 are also on similiar lines with those in 2018.




3. Correlation between 2017 US Mexico deaths vs North Africa -


```{r}
cor.test(head(US_M_2017$freqmU2,6),head(NA_M_2017$freqM2,6))
```

The number of deaths in 2017 at US-Mexico have very less correlation to those at North Africa.


Data Visualisation -


1. Visualising the causes of deaths at North Africa (Year-wise) :

```{r,include=FALSE}
migrant_NA_cau <-migrant_NA %>%
  dplyr::select(Reported.Year,Cause.of.Death,Number.Dead) %>%
  group_by(Reported.Year,Cause.of.Death) %>%
  summarise(s=sum(Number.Dead,na.rm=1))
   

na2016=migrant_NA_cau %>%
  dplyr::filter(Reported.Year==2016)
na2017=migrant_NA_cau %>%
  dplyr::filter(Reported.Year==2017)
na2018=migrant_NA_cau %>%
  dplyr::filter(Reported.Year==2018)
na2019=migrant_NA_cau %>%
  dplyr::filter(Reported.Year==2019)

na2016=head(na2016[order(na2016$s,decreasing=TRUE),],4)
na2017=head(na2017[order(na2017$s,decreasing=TRUE),],4)
na2018=head(na2018[order(na2018$s,decreasing=TRUE),],4)
na2019=head(na2019[order(na2019$s,decreasing=TRUE),],4)



n1=ggplot(na2016,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity')+
  ggtitle('2016')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)+
  theme(legend.text=element_text(size=5))

n2=ggplot(na2017,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity')+
  ggtitle('2017')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)+
  theme(legend.text=element_text(size=5))

n3=ggplot(na2018,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity',size=5)+
  ggtitle('2018')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)+
  theme(legend.text=element_text(size=5))

n4=ggplot(na2019,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity')+
  ggtitle('2019')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)+
  theme(legend.text=element_text(size=5))

```
```{r,fig.width=8,fig.height=6,echo=FALSE}
grid.arrange(n1,n2,n3,n4 ,
             top = textGrob('Causes of deaths at North Africa'))
  
```

It can be observed that -

1. Most of the people died due to sickness in 2016.
2. More deaths were due to vehicle accidents and drowning in 2017.
3. In 2018, more people died due sickness and lack of medicinal access.
4. In 2019, the major cause of death was Hypothermia.


2. Visualising the causes of death at Mediterranenean

```{r,include=FALSE}
migrant_M=migrant_df %>%
  dplyr::filter(Region.of.Incident=='Mediterranean')

migrant_M_cau <-migrant_M %>%
  dplyr::select(Reported.Year,Cause.of.Death,Number.Dead) %>%
  group_by(Reported.Year,Cause.of.Death) %>%
  summarise(s=sum(Number.Dead,na.rm=1))


m2016=migrant_M_cau %>%
  dplyr::filter(Reported.Year==2016)
m2017=migrant_M_cau %>%
  dplyr::filter(Reported.Year==2017)
m2018=migrant_M_cau %>%
  dplyr::filter(Reported.Year==2018)
m2019=migrant_M_cau %>%
  dplyr::filter(Reported.Year==2019)

m2016=head(m2016[order(m2016$s,decreasing=TRUE),],4)
m2017=head(m2017[order(m2017$s,decreasing=TRUE),],4)
m2018=head(m2018[order(m2018$s,decreasing=TRUE),],4)
m2019=head(m2019[order(m2019$s,decreasing=TRUE),],4)


m1=ggplot(m2016,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity')+
  ggtitle('2016')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)

m2=ggplot(m2017,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity')+
  ggtitle('2017')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)

m3=ggplot(m2018,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity')+
  ggtitle('2018')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)

m4=ggplot(m2019,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity')+
  ggtitle('2019')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)

```
```{r,fig.width=8,fig.height=6,echo=FALSE}
grid.arrange(m1,m2,m3,m4 ,
             top = textGrob('Causes of deaths at Mediterranen'))
```

It can be implied from this graph that most of the deaths at Mediterranenean occured due to drowning in all those years, this is because of presence of oceans and seas at the migration routes.

3. Visualising death causes at US Mexico border -

```{r,include=FALSE}
migrant_US_cau <-migrant_US %>%
  dplyr::select(Reported.Year,Cause.of.Death,Number.Dead) %>%
  group_by(Reported.Year,Cause.of.Death) %>%
  summarise(s=sum(Number.Dead,na.rm=1))


us2016=migrant_US_cau %>%
  dplyr::filter(Reported.Year==2016)
us2017=migrant_US_cau %>%
  dplyr::filter(Reported.Year==2017)
us2018=migrant_US_cau %>%
  dplyr::filter(Reported.Year==2018)
us2019=migrant_US_cau %>%
  dplyr::filter(Reported.Year==2019)

us2016=head(us2016[order(us2016$s,decreasing=TRUE),],4)
us2017=head(us2017[order(us2017$s,decreasing=TRUE),],4)
us2018=head(us2018[order(us2018$s,decreasing=TRUE),],4)
us2019=head(us2019[order(us2019$s,decreasing=TRUE),],4)


uc1=ggplot(us2016,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity')+
  ggtitle('2016')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)

uc2=ggplot(us2017,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity')+
  ggtitle('2017')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)

uc3=ggplot(us2018,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity')+
  ggtitle('2018')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)

uc4=ggplot(us2019,aes(x=2,s,fill=Cause.of.Death))+
  geom_bar(width=1,stat='identity')+
  ggtitle('2019')+
  coord_polar("y",start=0)+
  theme_void()+
  xlim(0.5,2.5)

```
```{r,fig.width=8,fig.height=6,,echo=FALSE}
grid.arrange(uc1,uc2,uc3,uc4 ,
             top = textGrob('Causes of deaths at US Mexico Border'))


```
It can be inferred from the donut graphs the reason of the occurence of most deaths was unknown and their skeletons were found. Although there were few cases where people died due to drowning.

2. Visualising the number of incidents on prominent regions -


```{r,include=FALSE}
m_reg <- migrant_df %>%
  dplyr::select(WebID,Reported.Year,Region.of.Incident) %>%
  group_by(Reported.Year,Region.of.Incident) %>%
  summarise(count=n())

m_reg2016 <- m_reg %>%
  dplyr::filter(Reported.Year==2016)
m_reg2017 <- m_reg %>%
  dplyr::filter(Reported.Year==2017)
m_reg2018 <- m_reg %>%
  dplyr::filter(Reported.Year==2018)
m_reg2019 <- m_reg %>%
  dplyr::filter(Reported.Year==2019)


m_reg2016=head(m_reg[order(m_reg2016$count,decreasing = TRUE),],4)
m_reg2017=head(m_reg[order(m_reg2017$count,decreasing = TRUE),],4)
m_reg2018=head(m_reg[order(m_reg2018$count,decreasing = TRUE),],4)
m_reg2019=head(m_reg[order(m_reg2019$count,decreasing = TRUE),],4)



mreg16=ggplot(m_reg2016,aes(Region.of.Incident,count))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Regions of incident',y='Count')+
  ggtitle('2016')
mreg17=ggplot(m_reg2017,aes(Region.of.Incident,count))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Regions of incident',y='Count')+
  ggtitle('2017')
mreg18=ggplot(m_reg2018,aes(Region.of.Incident,count))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Regions of incident',y='Count')+
  ggtitle('2018')
mreg19=ggplot(m_reg2019,aes(Region.of.Incident,count))+
  geom_bar(stat='identity',fill='steelblue')+
  labs(x='Regions of incident',y='Count')+
  ggtitle('2019')

```
```{r,fig.width=10,fig.height=6,,echo=FALSE}
grid.arrange(mreg16,mreg17,mreg18,mreg19 ,
             top = textGrob('Yearwise number of incidents'))

```
From the bar chart, we can state few observations that -

In 2016, most of the incidents were reported in Europe and Horn of Africa. However in 2017 the rise of incidents around Mediterranenean increased rapidly and most incidents took place on the same migration route. This trend was followed in 2018 and 2019.

3. Visualising the number of deaths per year over different regions -

```{r,include=FALSE}
mg_d_US <- migrant_US %>%
  dplyr::filter(Reported.Year,Number.Dead) %>%
  group_by(Reported.Year) %>%
  summarise(s=sum(Number.Dead))

mg_d_M <- migrant_M %>%
  dplyr::filter(Reported.Year,Number.Dead) %>%
  group_by(Reported.Year) %>%
  summarise(s=sum(Number.Dead))

mg_d_NA <- migrant_NA %>%
  dplyr::filter(Reported.Year,Number.Dead) %>%
  group_by(Reported.Year) %>%
  summarise(s=sum(Number.Dead))

migrantSaharan <- migrant_df %>%
  dplyr::filter(Region.of.Incident=='Sub-Saharan Africa')

mg_d_SA <- migrantSaharan %>%
  dplyr::filter(Reported.Year,Number.Dead) %>%
  group_by(Reported.Year) %>%
  summarise(s=sum(Number.Dead))


mgd1=ggplot(mg_d_US,aes(Reported.Year,s))+
  geom_line(color='red')+
  labs(x='Year',y='Number of deaths')+
  ggtitle('US Mexico Border')+
  theme(plot.title = element_text(size = 10))

mgd2=ggplot(mg_d_NA,aes(Reported.Year,s))+
  geom_line(color='red')+
  labs(x='Year',y='Number of deaths')+
  ggtitle('North Africa')+
  theme(plot.title = element_text(size = 10))

mgd3=ggplot(mg_d_SA,aes(Reported.Year,s))+
  geom_line(color='red')+
  labs(x='Year',y='Number of deaths')+
  ggtitle('SubSaharan Africa')+
  theme(plot.title = element_text(size = 10))

mgd4=ggplot(mg_d_M,aes(Reported.Year,s))+
  geom_line(color='red')+
  labs(x='Year',y='Number of deaths')+
  ggtitle('Mediterranean')+
  theme(plot.title = element_text(size = 10))

```
```{r,echo=FALSE}
grid.arrange(mgd1,mgd2,mgd3,mgd4 ,
             top = textGrob('Yearwise number of deaths',gp=gpar(fontsize=15)))

```

It can be observed that number of deaths kept increasing till 2018 at US Mexico border and sharply decreasing till 2019. The highest number of deaths occured in 2016 at North Africa region. SUb Saharan Africa region recorded no deaths in 2019 after having maximum number of deaths in 2018. The Mediterranean region deaths also significantly reduced from 2015 to 2019.



4. Visualising and Comparing Male/Female deaths across different regions -


```{r,include=FALSE}
FM_NA <-migrant_NA %>%
  dplyr::select(Reported.Year,Number.of.Males,Number.of.Females) %>%
  group_by(Reported.Year) %>%
  summarise(Male=sum(Number.of.Males,na.rm=1),Female=sum(Number.of.Females,na.rm=1))   


x=melt(FM_NA,id=c(1),measure=c(2:3))


mf1=ggplot(x,aes(x=Reported.Year,y=value,fill=variable)) + 
  geom_bar(position = 'dodge',stat='identity')+
  labs(x='Year',y='Num of Deaths')+
  ggtitle('North Africa')+
  theme(plot.title = element_text(size = 10))

#Mediterranean
FM_M <-migrant_M %>%
  dplyr::select(Reported.Year,Number.of.Males,Number.of.Females) %>%
  group_by(Reported.Year) %>%
  summarise(Male=sum(Number.of.Males,na.rm=1),Female=sum(Number.of.Females,na.rm=1))   


x1=melt(FM_M,id=c(1),measure=c(2:3))


mf2=ggplot(x1,aes(x=Reported.Year,y=value,fill=variable)) + 
  geom_bar(position = 'dodge',stat='identity')+
  labs(x='Year',y='Num of Deaths')+
  ggtitle('Mediterranean')+
  theme(plot.title = element_text(size = 10))

#US Mexico Border

FM_U <-migrant_US %>%
  dplyr::select(Reported.Year,Number.of.Males,Number.of.Females) %>%
  group_by(Reported.Year) %>%
  summarise(Male=sum(Number.of.Males,na.rm=1),Female=sum(Number.of.Females,na.rm=1))   


x2=melt(FM_U,id=c(1),measure=c(2:3))


mf3=ggplot(x2,aes(x=Reported.Year,y=value,fill=variable)) + 
  geom_bar(position = 'dodge',stat='identity')+
  labs(x='Year',y='Num of Deaths')+
  ggtitle('US Mexico Border')+
  theme(plot.title = element_text(size = 10))

#Sub Saharan -

FM_SA <-migrantSaharan %>%
  dplyr::select(Reported.Year,Number.of.Males,Number.of.Females) %>%
  group_by(Reported.Year) %>%
  summarise(Male=sum(Number.of.Males,na.rm=1),Female=sum(Number.of.Females,na.rm=1))   


x3=melt(FM_SA,id=c(1),measure=c(2:3))


mf4=ggplot(x3,aes(x=Reported.Year,y=value,fill=variable)) + 
  geom_bar(position = 'dodge',stat='identity')+
  labs(x='Year',y='Num of Deaths')+
  ggtitle('SubSaharan Africa')+
  theme(plot.title = element_text(size = 10))

```
```{r,echo=FALSE,fig.width=9,fig.height=6}
grid.arrange(mf1,mf2,mf3,mf4 ,
             top = textGrob('Comparison of Male/Female Deaths',gp=gpar(fontsize=15)))
```

Across different geographic regions, it can be noted that the death count of males in comparison to females was more for every year. However in Sub Saharan region, during 2015 more females died.

```{r,include=FALSE}
#######################################################
library(mapview)
df = read.csv("MissingMigrants-Global-2019-03-29T18-36-07.csv",header = TRUE,# the dataset has header columns
              sep = ',')

#north america
df_NA<- df %>%
  dplyr::filter(Region.of.Incident=='US-Mexico Border')

df_NA$lan <- str_replace(str_extract(df_NA$Location.Coordinates, ".*,"), ",", "")
df_NA$lon <- str_trim(str_replace(str_extract(df_NA$Location.Coordinates, ",.*"), ",", ""))
df_NA$lon <- as.numeric(df_NA$lon)
df_NA$lan<- as.numeric(df_NA$lan)

US_Mexico_Border <- df_NA[, c('lan','lon')]

# There cannot be any missings before transformation
US_Mexico_Border[is.na(US_Mexico_Border$lan), 'lan'] <- 0
US_Mexico_Border[is.na(US_Mexico_Border$lon), 'lon'] <- 0

# We convert an object st as sf, which is needed for later operations
US_Mexico_Border <- sf::st_as_sf(US_Mexico_Border, coords=c("lon","lan"), crs=4326)

df_M<- df %>%
  dplyr::filter(Region.of.Incident=='Mediterranean')

df_M$lan <- str_replace(str_extract(df_M$Location.Coordinates, ".*,"), ",", "")
df_M$lon <- str_trim(str_replace(str_extract(df_M$Location.Coordinates, ",.*"), ",", ""))
df_M$lon <- as.numeric(df_M$lon)
df_M$lan<- as.numeric(df_M$lan)

Mediterrranean <- df_M[, c('lan','lon')]

# There cannot be any missings before transformation
Mediterrranean[is.na(Mediterrranean$lan), 'lan'] <- 0
Mediterrranean[is.na(Mediterrranean$lon), 'lon'] <- 0

# We convert an object st as sf, which is needed for later operations
Mediterrranean <- sf::st_as_sf(Mediterrranean, coords=c("lon","lan"), crs=4326)



######################
#sub-saharan Africa


df_sub_saharan_Africa<- df %>%
  dplyr::filter(Region.of.Incident=='Sub-Saharan Africa')

df_sub_saharan_Africa$lan <- str_replace(str_extract(df_sub_saharan_Africa$Location.Coordinates, ".*,"), ",", "")
df_sub_saharan_Africa$lon <- str_trim(str_replace(str_extract(df_sub_saharan_Africa$Location.Coordinates, ",.*"), ",", ""))
df_sub_saharan_Africa$lon <- as.numeric(df_sub_saharan_Africa$lon)
df_sub_saharan_Africa$lan<- as.numeric(df_sub_saharan_Africa$lan)

Sub_saharan_Africa <- df_sub_saharan_Africa[, c('lan','lon')]

# There cannot be any missings before transformation
Sub_saharan_Africa[is.na(Sub_saharan_Africa$lan), 'lan'] <- 0
Sub_saharan_Africa[is.na(Sub_saharan_Africa$lon), 'lon'] <- 0

# We convert an object st as sf, which is needed for later operations
Sub_saharan_Africa <- sf::st_as_sf(Sub_saharan_Africa, coords=c("lon","lan"), crs=4326)



#########################

#NorthAfrica

df_sub_north_Africa<- df %>%
  dplyr::filter(Region.of.Incident=='North Africa')

df_sub_north_Africa$lan <- str_replace(str_extract(df_sub_north_Africa$Location.Coordinates, ".*,"), ",", "")
df_sub_north_Africa$lon <- str_trim(str_replace(str_extract(df_sub_north_Africa$Location.Coordinates, ",.*"), ",", ""))
df_sub_north_Africa$lon <- as.numeric(df_sub_north_Africa$lon)
df_sub_north_Africa$lan<- as.numeric(df_sub_north_Africa$lan)

North_Africa <- df_sub_north_Africa[, c('lan','lon')]

# There cannot be any missings before transformation
North_Africa[is.na(North_Africa$lan), 'lan'] <- 0
North_Africa[is.na(North_Africa$lon), 'lon'] <- 0

# We convert an object st as sf, which is needed for later operations
North_Africa <- sf::st_as_sf(North_Africa, coords=c("lon","lan"), crs=4326)

```
































































































































































